---
title: "Overview of dissolved organic carbon"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 7, fig.align = "center")

#<><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
# FILE:         main.R
#
# AUTHOR:       Philippe Massicotte
#
# DESCRIPTION:  Load packages and setup for the project.
#<><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>

# Setup -------------------------------------------------------------------

library(extrafont)
library(tidyverse)
library(GGally)

rm(list = ls())
graphics.off()

## Set default ggplot2 font size and font family

loadfonts(quiet = TRUE)
theme_set(theme_bw(base_size = 10, base_family = "Open Sans"))

raimbault <- readxl::read_excel("doc.xlsx", sheet = 1) %>% 
  janitor::clean_names() %>% 
  select(
    jday = station,
    depth,
    doc
  ) %>% 
  mutate(source = "raimbault")

christos <- readxl::read_excel("doc.xlsx", sheet = 2) %>% 
  janitor::clean_names() %>% 
  select(
    jday = station,
    depth,
    doc
  ) %>% 
  mutate(source = "christos") %>% 
  filter(doc != 139) 

atsushi <- readxl::read_excel("doc.xlsx", sheet = 3) %>% 
  janitor::clean_names() %>% 
  select(
    jday = julian_day,
    depth = depth_m,
    doc = doc_umol_l
  ) %>% 
  mutate(source = "atsushi")

df <- bind_rows(raimbault, christos, atsushi) %>% 
  drop_na(jday, depth, doc)


```

## Time series

Overview of the time series from the three sources of DOC.

```{r}
df %>% 
  group_by(depth) %>% 
  filter(n() > 1) %>% 
  ggplot(aes(x = jday, y = doc, color = source)) +
  geom_point() +
  geom_line() +
  facet_wrap(~depth) +
  labs(title = "Time series of DOC. Numbers in gray boxes are the depths (meters)")
```

## Vertical profiles

DOC vertical profiles per day.

```{r, fig.width=10, fig.height=8}
df %>% 
  ggplot(aes(x = doc, y = depth, color = source)) +
  geom_point() +
  geom_path() +
  facet_wrap(~jday, scales = "free_y") +
  scale_y_reverse() +
  labs(title = "Numbers in gray boxes are the julian days")
```


## Boxplots

The following boxplot compares the median values of the three DOC sources. Visually, is seems that Atsushi DOC values are a bit lower compared to other sources.

```{r, fig.height=4, fig.width=5}
df %>% 
  ggplot(aes(x = source, y = doc)) +
  geom_boxplot()
```

A simple ANOVA shows that there is at least one group different among the three.

```{r}
mod <- aov(doc ~ source, data = df)
knitr::kable(broom::tidy(mod))
```

Refining the previous ANOVA analysis, the Tukey Honest differences shows that indeed Christos and Raimbault DOC are on average 7.23 and 9.01 $\mu$~mol higher than that of Atsushi. On other hand, there is no significant different difference between Raimvault and Christos DOC values even thought they are not correlated (see bellow).  

```{r}
knitr::kable(broom::tidy(TukeyHSD(mod)))
```

The following graphs explore the differences by depths.

```{r}
df %>% 
  group_by(depth) %>% 
  filter(n_distinct(source) > 1) %>% 
  ggplot(aes(x = source, y = doc, group = source)) +
  geom_boxplot(size = 0.25, width = 0.8) +
  facet_wrap(~depth)
```

## Correlations

Based on the following graphs, there is not much correlation between the three DOC sources.

```{r}
df %>% 
  spread(source, doc) %>% 
  ggpairs(columns = 3:5) +
  labs(title = "Correlation plots between the three DOC sources")
  
```

### Atsushi vs Raimbault

```{r, fig.width=8, fig.height=3}
df %>% 
  spread(source, doc) %>% 
  drop_na() %>% 
  group_by(depth) %>% 
  filter(n() > 1) %>% 
  ggplot(aes(x = atsushi, y = raimbault)) +
  geom_point() +
  facet_wrap(~depth, scales = "free") +
  geom_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  labs(title = "Correlation by depth with 1:1 line (dashed). Number in top graybox is the sampling depth.")
```

### Atsushi vs Christos

```{r, fig.width=8, fig.height=3}
df %>% 
  spread(source, doc) %>% 
  drop_na() %>% 
  group_by(depth) %>% 
  filter(n() > 1) %>% 
  ggplot(aes(x = atsushi, y = christos)) +
  geom_point() +
  facet_wrap(~depth, scales = "free") +
  geom_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  labs(title = "Correlation by depth with 1:1 line (dashed). Number in top graybox is the sampling depth.")
```

### Christos vs Raimbault

```{r, fig.width=8, fig.height=3}
df %>% 
  spread(source, doc) %>% 
  drop_na() %>% 
  group_by(depth) %>% 
  filter(n() > 1) %>%
  ggplot(aes(x = christos, y = raimbault)) +
  geom_point() +
  facet_wrap(~depth, scales = "free") +
  geom_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  labs(title = "Correlation by depth with 1:1 line (dashed). Number in top graybox is the sampling depth.")
```

## Correlation with CDOM data

The next graph shows the relationships between DOC and CDOM absorption (m-1) at 5 wavelengths (250, 300, 350, 400 and 450 nm). As we can see, there are no relations between DOC and aCDOM. 

```{r, fig.width=8}
cdom <- read_csv("../../data/clean/cdom_ice_camp_2016.csv") %>% 
  filter(water_type == "wat") %>% 
  select(jday, wavelength, to_depth, absorption) %>% 
  mutate(depth = parse_number(to_depth))

res <- inner_join(df, cdom)

res %>% 
  filter(wavelength %in% c(250, 300, 350, 400, 450)) %>% 
  ggplot(aes(x = absorption, y = doc)) +
  geom_point(aes(color = factor(depth))) +
  facet_grid(source ~ wavelength, scales = "free") +
  geom_smooth(method = "lm") +
  labs(color = "Depth (m)")
    

```

