---
title: "Historic of sea ice concentration"
author: "Philippe Massicotte"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
    latex_engine: xelatex
  # word_document: default
mainfont: Open Sans
fontsize: 12
---

```{r, message=FALSE, echo=FALSE}
library(tidyverse)

library(extrafont)
loadfonts(quiet = TRUE)
theme_set(theme_bw(base_size = 10, base_family = "Open Sans"))


df <- readr::read_csv("../../data/clean/ice_history.csv")

```

This document presents an overview of the methodology used to extract the historic of sea ice concentration of the stations visited by the Amundsen in 2016 (project Green Edge).

## Data

Sea ice concentration has been extracted from AMSR2 radiometer on a 3.125 km grid. At each Amundsen station, the historic of sea ice concentration was extracted between 2016-03-01 and 2016-07-14. Sea ice concentration was extracted form the closest pixel using the Eucledian distance between ship position and the center of each pixel.

## Example

This is an example for station **G104**.

```{r, echo = FALSE, fig.align='center'}
df %>% 
  filter(station == "G104") %>% 
  ggplot(aes(x = ice_date, y = sic * 100)) +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Sea ice concentration (%)") +
  scale_x_date(date_labels = "%Y-%m-%d")
```

## Average sea ice concentration

This is the averaged ($\pm$ S.D.) sea ice concentration between 2016-03-01 and 2016-07-14

```{r, echo = FALSE, fig.align='center'}
df2 <- df %>% 
  group_by(ice_date) %>% 
  summarise(
    mean_sic = mean(sic * 100, na.rm = TRUE),
    sd_sic = sd(sic * 100, na.rm = TRUE)
  )

df2 %>% 
  ggplot(aes(x = ice_date, y = mean_sic)) +
  geom_ribbon(aes(ymin = mean_sic - sd_sic, ymax = mean_sic + sd_sic), fill = "gray75", alpha = 0.5) +
  geom_line() +
  xlab("Date") +
  ylab("Mean sea ice concentration (%)") +
  scale_x_date(date_labels = "%Y-%m-%d")

```


## How to cite the data

If you use this dataset please cite University of Hamburg and the following article:

Beitsch, A.; Kaleschke, L.; Kern, S. Investigating High-Resolution AMSR2 Sea Ice Concentrations during the February 2013 Fracture Event in the Beaufort Sea. Remote Sens. 2014, 6, 3841-3856, doi:10.3390/rs6053841

Paper Open Access available online: http://www.mdpi.com/2072-4292/6/5/3841

For citations of the data itself you may use:

Kaleschke, L. and X. Tian-Kunze (2016), "AMSR2 ASI 3.125 km Sea Ice Concentration Data, V0.1", Institute of Oceanography, University of Hamburg, Germany, digital media (ftp-projects.zmaw.de/seaice/), [BEGIN DAY/MONTH/YEAR - END DAY/MONTH/YEAR].

## Detailed information

Detailed information can be found in the following official README file: ftp://ftp-projects.zmaw.de/seaice/AMSR2/README.txt
